A Partitioning Algorithm for Maximum Common Subgraph Problems\thanks{This work was supported by a pile of money from a funding agency.}

### 2017-02-16 paper/paper.tex
Subfigured algorithm example tables

\usepackage{ijcai17}
\usepackage{times}
\usepackage{graphicx}
\usepackage{cleveref}
\usepackage{microtype}

@@

% cref style
\crefname{algorithm}{Algorithm}{Algorithms}
\Crefname{algorithm}{Algorithm}{Algorithms}
\crefname{algocf}{Algorithm}{Algorithms}
\Crefname{algocf}{Algorithm}{Algorithms}
\crefname{figure}{Figure}{Figures}
\Crefname{figure}{Figure}{Figures}
\crefname{table}{Table}{Tables}
\Crefname{table}{Table}{Tables}
\crefname{section}{Section}{Sections}
\Crefname{section}{Section}{Sections}

@@

With these definitions established, we now present \McSplit, a branch and bound
algorithm which uses a new vertex-labelling scheme to avoid explicitly
maintaining the set of feasible mappings for each vertex in $\V(G)$.

\McSplit\ finds a maximum-cardinality mapping $M^* = \{(v_1, w_1), \dots,
(v_{m}, w_{m})\}$ with $|M^*| = m$ vertex pairs, where the $v_i$ are distinct members of $\V(G)$ and the
$w_i$ are distinct vertices of $\V(H)$, such that $v_i$ and $v_j$ are adjacent
in $G$ if and only if $w_i$ and $w_j$ are adjacent in $H$. 
Given such a mapping, the subgraph of $G$ induced by $\{v_i, \dots, v_{m}\}$
and the subgraph of $H$ induced by $\{w_i, \dots, w_{m}\}$ are a maximum
common subgraph.

Before discussing the algorithm in detail, we start with an illustration of the
main concepts using the graphs $G$ and $H$ in \cref{fig:alg1}.  These graphs
have a maximum common subgraph with four vertices; one example is the mapping
$\{1a, 2f, 3d, 5b\}$ where vertex $1$ is assigned to vertex $a$, $2$ is
assigned to $f$, $3$ to $d$ and $5$ to $b$.

@@

?? Talk about how we can use a pair of flat arrays and indices to the start of
label classes, and throw in citation to partition backtracking here.

>>>>

\usepackage{ijcai17}
\usepackage{times}
\usepackage{graphicx}
\usepackage{cleveref}

@@

% cref style
\crefname{algorithm}{Algorithm}{Algorithms}
\Crefname{algorithm}{Algorithm}{Algorithms}
\crefname{figure}{Figure}{Figures}
\Crefname{figure}{Figure}{Figures}
\crefname{table}{Table}{Tables}
\Crefname{table}{Table}{Tables}
\crefname{section}{Section}{Sections}
\Crefname{section}{Section}{Sections}

@@

With these definitions established, we now present \McSplit, a branch and bound
algorithm which uses a new vertex-labelling scheme to avoid explicitly
maintaining the set of feasible mappings for each vertex in $\V(G)$.
\iffalse
As we will explore in
\cref{sec:comparison}, the algorithm may be viewed as a version of the
constraint programming forward-checking (CP-FC) algorithm using a compact data
structure that exploits the nature of the MCS problem.  It is sufficiently
different, however, that it is helpful to describe the algorithm without
reference to previous approaches.

%At each node of the search tree, the algorithm
%labels vertices in $\V(G)$ and $\V(H)$ such that a pair $(v, w)$ with $v \in
%\V(G)$ and $w \in \V(H)$ can be added to the mapping if and only if $v$ and $w$
%have the same label.
\fi
\McSplit\ finds a maximum-cardinality mapping $M^* = \{(v_1, w_1), \dots,
(v_{m}, w_{m})\}$ with $|M^*| = m$ vertex pairs, where the $v_i$ are distinct members of $\V(G)$ and the
$w_i$ are distinct vertices of $\V(H)$, such that $v_i$ and $v_j$ are adjacent
in $G$ if and only if $w_i$ and $w_j$ are adjacent in $H$. 
Given such a mapping, the subgraph of $G$ induced by $\{v_i, \dots, v_{m}\}$
and the subgraph of $H$ induced by $\{w_i, \dots, w_{m}\}$ are a maximum
common subgraph.

We will use the graphs $G$ and $H$ in \cref{fig:alg1} to demonstrate the
algorithm.  These graphs have a maximum common subgraph with four vertices; one
example is the mapping $\{1a, 2f, 3d, 5b\}$ where vertex $1$ is assigned to
vertex $a$, $2$ is assigned to $f$, $3$ to $d$ and $5$ to $b$.

@@
